### 2013-06-25 Tex/chapters/results.tex
Definitionen hinyugefuegt

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetisation per site \(m\) and energy per site \(E\)
are calculated and saved for every \(2\tau\) sweeps. Where \(\tau\)
denotes the \emph{autocorrelation time} (see also \ref{ssec:eqtime}).
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
random proximity graphs with the same disorder paramter \(\sigma\)
are then averaged to \(\overline{\avg{O}}\). The errors are estimated
by bootstrapping \cite{Bootstrap}.

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}).
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
random proximity graphs with the same disorder paramter \(\sigma\)
are then averaged to \(\overline{\avg{O}}\). The errors are estimated
by bootstrapping \cite{Bootstrap}.
